Distributed lag effects of smoke on cardiovascular disease in persons over 65

### 2017-11-21 r_scripts/analysis/oregon_cvd_dl_over65_results.Rmd
adding function to find spline of best fit.

@@

@@

>>>>

  # if degrees of freedom for pm is defined
  if(length(pm_df)==1){

@@

  }

  # if degrees of freedom is a vector > 1
  pm_df <- c(2:5)

  if(pm_df > 1){
  # create temp basis
    temp_b <- splines::ns(0:(ncol(temp_matrix)-1), df=temp_df, intercept=T)
    temp_basis <- temp_matrix %*% temp_b
  # create list of lengh pm_df
  mod_aic <- sapply(pm_df, function(x){
    pm_b <- splines::ns(0:(ncol(pm_matrix)-1), df=x, intercept=T)
    # create pm basis
    pm_basis <- pm_matrix %*% pm_b
    # run model
    mod <- clogit(outcome ~ pm_basis + temp_basis + strata(personkey),
    data = complete_data)
    aic <- AIC(mod)
    return(aic)
  })

  # find minimum aic
  pm_df_aic <- data.frame(pm_df, mod_aic)
  min_df_aic <- as.numeric(subset(pm_df_aic, mod_aic == min(mod_aic), 
                                  select=pm_df))
  # run final best fit mod
  pm_b <- splines::ns(0:(ncol(pm_matrix)-1), df=min_df_aic, intercept=T)
  # create pm basis
  pm_basis <- pm_matrix %*% pm_b
  # run model
  mod <- clogit(outcome ~ pm_basis + temp_basis + strata(personkey),
    data = complete_data)
  }

@@

```{r mi data}
mi65 <- outcome_df_list[[6]] %>% 
  filter(age_ind == 2)

cumulative <- distributed_lag(mi65, pm_df = 2, temp_df = 2, cumulative = T)
cumulative

#plot 
cumulative_plot <- ggplot(cumulative, aes(x=time, y=estimate)) +
  geom_line(colour = "#046C9A", size = 1) +
  geom_ribbon(aes(ymin = lower95, ymax = upper95), 
              fill = "#ABDDDE", alpha = 0.5) + 
  scale_y_continuous(limits = c(0.7, 1.2)) +
  scale_x_continuous(breaks = c(seq(0,7, by=1))) +
  geom_hline(yintercept = 1, linetype = 2, colour = "red") +
  ylab(expression("Odd ratio for a 10 ug/m^3 increase smoke PM"[2.5])) +
  xlab("Lagged Days") +
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    strip.text = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_rect(colour=NA, fill=NA))

dl <- distributed_lag(mi65, pm_df = 3, temp_df = 2, cumulative = F)
dl
